---
title: "swiftkey"
author: "Sebastien Plat"
output: html_document
---

```{r}
setwd('D:\\datascienceCapstone')
install.packages("RWeka") # tokenization in N-grams
install.packages("qdap")  # spelling check
require(dplyr)
```


### build a 10% sample 

```{r}
# sampling - 15 sec
source('./helpers/sampleCleaner.R')
sampleCleaner("en_US", "blogs", 1)
``` 


### Fast tokenization & unique word list

```{r}
# fast tokenization - 10sec
source('./helpers/fastTokenizer.R') # custom split: remove ', add =<>~*&_/\ plus numbers
ptm <- proc.time()
src <- "./data/en_US.blogs.sample10.txt"
dest <- "./data/newsUS_sample" # '_Gx.Rds' is appended to the file name
G1_list <- fastTokenize(src, dest, 1, 'full')
proc.time() - ptm
rm(src,dest,fastTokenize)
length(G1_list)

# unique words frequency - 5sec
ptm <- proc.time()
G1_freq <- data.frame(table(G1_list))
G1_freq <- arrange(G1_freq, desc(Freq))
proc.time() - ptm


# remove non-words
G1r <- grepl("â", G1_freq[,1])
length(G1r)
head(G1_freq[G1r==TRUE, ], 10)
sum(G1_freq[G1r==TRUE, 2])
length(G1_freq[G1r==TRUE, 2])

G1_freq <- G1_freq[G1r==TRUE, ]
rm(G1r)
``` 


### Replace unknown words (from qdap dictionary)

```{r}
require(qdap)
source('./helpers/dictLister.R')

# build dict list from qdap dictionary - 1sec
dict <- qdapDictionaries::GradyAugmented
dictList <- createDictList(dict) # split the dict in a list of 26 elements

# filter unique words not in the qdap dictionary - 25sec
ptm <- proc.time()
wordList <- as.character(G1_freq[,1])
unknownWords <- getUnknownWords(wordList, dictList)
proc.time() - ptm

# show top unknown words
G1_freq_unknownWords <- G1_freq[unknownWords == TRUE, ]
saveRDS(G1_freq_unknownWords, "./data/twitter_unknownFreq.Rds")
head(G1_freq_unknownWords, 20)
sum(G1_freq_unknownWords[1:1000,2])

# identify positions of unknown words in the tokenized sample - 600sec
ptm <- proc.time()
unknownDictList <- createDictList(as.character(G1_freq_unknownWords[, 1]))
unknownTokens <- getUnknownWords(G1_list, unknownDictList, TRUE)
proc.time() - ptm

# replace all unkwnon tokens by "<UNK>"
G1_list[unknownTokens == TRUE] <- "<UNK>"
head(G1_list,100)
G1_freq <- data.frame(table(G1_list))
G1_freq <- arrange(G1_freq, desc(Freq))
head(G1_freq)
rm (createDictList, getUnknownWords, dict, dictList, wordList, unknownWords, unknownDictList, unknownTokens)

ptm <- proc.time()
text <- paste(gsub("eol#","\n",G1_list), collapse=" ")
text <- gsub(" \n "," \n", text)   
writeLines(text, "./data/twitterUS_sampleClean.txt")
proc.time() - ptm
  
```











### build a 10% sample 

```{r}
# sampling - 15 sec
source('./helpers/sampler.R')
ptm <- proc.time()
sample("./data/en_US/en_US.blogs.txt", "./data/blogUS_sample.txt", 10)
proc.time() - ptm
rm(sample)
``` 


### Fast tokenization & unique word list

```{r}
# fast tokenization - 10sec
source('./helpers/fastTokenizer.R') # custom split: remove ', add =<>~*&_/\ plus numbers
ptm <- proc.time()
src <- "./data/blogUS_sample.txt"
dest <- "./data/blogUS_sample" # '_Gx.Rds' is appended to the file name
G1_list <- fastTokenize(src, dest, 1, 'full')
proc.time() - ptm
rm(src,dest,fastTokenize)

# unique words frequency - 5sec
ptm <- proc.time()
G1_freq <- data.frame(table(G1_list))
G1_freq <- arrange(G1_freq, desc(Freq))
proc.time() - ptm

# remove non-words
G1r <- grepl("^[^a-z0-9]+$", G1_freq[,1])
G1_freq <- G1_freq[G1r==FALSE, ]
rm(G1r)
``` 


### Replace unknown words (from qdap dictionary)

```{r}
require(qdap)
source('./helpers/dictLister.R')

# build dict list from qdap dictionary - 1sec
dict <- qdapDictionaries::GradyAugmented
dictList <- createDictList(dict) # split the dict in a list of 26 elements

# filter unique words not in the qdap dictionary - 25sec
ptm <- proc.time()
wordList <- as.character(G1_freq[,1])
unknownWords <- getUnknownWords(wordList, dictList)
proc.time() - ptm

# show top unknown words
G1_freq_unknownWords <- G1_freq[unknownWords == TRUE, ]
saveRDS(G1_freq_unknownWords, "./data/blog_unknownFreq.Rds")
head(G1_freq_unknownWords, 20)
sum(G1_freq_unknownWords[1:1000,2])

# identify positions of unknown words in the tokenized sample - 600sec
ptm <- proc.time()
unknownDictList <- createDictList(as.character(G1_freq_unknownWords[, 1]))
unknownTokens <- getUnknownWords(G1_list, unknownDictList, TRUE)
proc.time() - ptm

# replace all unkwnon tokens by "<UNK>"
G1_list[unknownTokens == TRUE] <- "<UNK>"
head(G1_list,100)
G1_freq <- data.frame(table(G1_list))
G1_freq <- arrange(G1_freq, desc(Freq))
head(G1_freq)
rm (createDictList, getUnknownWords, dict, dictList, wordList, unknownWords, unknownDictList, unknownTokens)

ptm <- proc.time()
text <- paste(gsub("eol#","\n",G1_list), collapse=" ")
text <- gsub(" \n "," \n", text)   
writeLines(text, "./data/blogUS_sampleClean.txt")
proc.time() - ptm
  
```








### Fast tokenization & unique word list

```{r}
# fast tokenization - 10sec
source('./helpers/fastTokenizer.R') # custom split: remove ', add =<>~*&_/\ plus numbers
ptm <- proc.time()
src <- "./data/en_US/en_US.news.txt"
dest <- "./data/newsUS" # '_Gx.Rds' is appended to the file name
G1_list <- fastTokenize(src, dest, 1, 'full')
proc.time() - ptm
rm(src,dest,fastTokenize)

# unique words frequency - 5sec
ptm <- proc.time()
G1_freq <- data.frame(table(G1_list))
G1_freq <- arrange(G1_freq, desc(Freq))
proc.time() - ptm

# remove non-words
G1r <- grepl("^[^a-z0-9]+$", G1_freq[,1])
G1_freq <- G1_freq[G1r==FALSE, ]
rm(G1r)
``` 


### Replace unknown words (from qdap dictionary)

```{r}
require(qdap)
source('./helpers/dictLister.R')

# build dict list from qdap dictionary - 1sec
dict <- qdapDictionaries::GradyAugmented
dictList <- createDictList(dict) # split the dict in a list of 26 elements

# filter unique words not in the qdap dictionary - 25sec
ptm <- proc.time()
wordList <- as.character(G1_freq[,1])
unknownWords <- getUnknownWords(wordList, dictList)
proc.time() - ptm

# show top unknown words
G1_freq_unknownWords <- G1_freq[unknownWords == TRUE, ]
saveRDS(G1_freq_unknownWords, "./data/news_unknownFreq.Rds")
head(G1_freq_unknownWords, 20)
sum(G1_freq_unknownWords[1:1000,2])

# identify positions of unknown words in the tokenized sample - 600sec
ptm <- proc.time()
unknownDictList <- createDictList(as.character(G1_freq_unknownWords[, 1]))
unknownTokens <- getUnknownWords(G1_list, unknownDictList, TRUE)
proc.time() - ptm

# replace all unkwnon tokens by "<UNK>"
G1_list[unknownTokens == TRUE] <- "<UNK>"
head(G1_list,100)
G1_freq <- data.frame(table(G1_list))
G1_freq <- arrange(G1_freq, desc(Freq))
head(G1_freq)
rm (createDictList, getUnknownWords, dict, dictList, wordList, unknownWords, unknownDictList, unknownTokens)

ptm <- proc.time()
text <- paste(gsub("eol#","\n",G1_list), collapse=" ")
text <- gsub(" \n "," \n", text)   
writeLines(text, "./data/newsUS_clean.txt")
proc.time() - ptm
  
```






### Fast tokenization & unique word list

```{r}
# fast tokenization - 10sec
source('./helpers/fastTokenizer.R') # custom split: remove ', add =<>~*&_/\ plus numbers
src <- "./data/full/full.txt"
dest <- "./data/full_sample" # '_Gx.Rds' is appended to the file name
``` 

```{r}
ptm <- proc.time()
G1_list <- fastTokenize(src, dest, 1, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
G1_freq <- data.frame(table(G1_list))
G1_freq <- arrange(G1_freq, desc(Freq))
proc.time() - ptm
``` 

```{r}
ptm <- proc.time()
G2_list <- fastTokenize(src, dest, 2, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
G2_freq <- data.frame(table(G2_list))
G2_freq <- arrange(G2_freq, desc(Freq))
proc.time() - ptm
``` 

```{r}
ptm <- proc.time()
G3_list <- fastTokenize(src, dest, 3, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
G3_freq <- data.frame(table(G3_list))
G3_freq <- arrange(G3_freq, desc(Freq))
proc.time() - ptm
``` 

```{r}
ptm <- proc.time()
G4_list <- fastTokenize(src, dest, 4, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
G4_freq <- data.frame(table(G4_list))
G4_freq <- arrange(G4_freq, desc(Freq))
proc.time() - ptm
``` 




### Fast tokenization & unique word list

```{r}
# fast tokenization - 10sec
source('./helpers/fastTokenizer.R') # custom split: remove ', add =<>~*&_/\ plus numbers
src <- "./data/full/fullClean.txt"
dest <- "./data/fullClean_sample" # '_Gx.Rds' is appended to the file name
``` 

```{r}
ptm <- proc.time()
GOK1_list <- fastTokenize(src, dest, 1, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
GOK1_freq <- data.frame(table(GOK1_list))
GOK1_freq <- arrange(GOK1_freq, desc(Freq))
proc.time() - ptm
``` 

```{r}
ptm <- proc.time()
GOK2_list <- fastTokenize(src, dest, 2, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
GOK2_freq <- data.frame(table(GOK2_list))
GOK2_freq <- arrange(GOK2_freq, desc(Freq))
proc.time() - ptm
``` 

```{r}
ptm <- proc.time()
GOK3_list <- fastTokenize(src, dest, 3, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
GOK3_freq <- data.frame(table(GOK3_list))
GOK3_freq <- arrange(GOK3_freq, desc(Freq))
proc.time() - ptm
``` 

```{r}
ptm <- proc.time()
GOK4_list <- fastTokenize(src, dest, 4, 'full')
proc.time() - ptm

# unique words frequency - 5sec
ptm <- proc.time()
GOK4_freq <- data.frame(table(GOK4_list))
GOK4_freq <- arrange(GOK4_freq, desc(Freq))
proc.time() - ptm


filter <- grepl("^make me the ",GOK4_freq[,1])
head(GOK4_freq[filter==TRUE,],10)

filter <- grepl("^on my ",GOK3_freq[,1])
head(GOK3_freq[filter==TRUE,],10)

head(GOK4_freq[grep("[^(unk)]",GOK4_freq),],10)
``` 



### frequency of frequencies

```{r}
GOK4_freq_freq <- data.frame(table(GOK4_freq[,2]))
cat <- sapply(GOK4_freq_freq[,1], function(x) {
  y <- as.numeric(x)
  if (y == 1) {
    return ("1")
  }
  else if (y <= 10) {
    return ("<=10")
  }
  else if (y <= 100) {
    return ("<=100")
  }
  else {
    return (">100")
  }
})
GOK4_freq_freq[, "cat"] <- cat
GOK4_freq_freq <- group_by(GOK4_freq_freq, cat) %>% summarize (Freq = sum(Freq))



GOK1_freq_freq
GOK2_freq_freq
GOK3_freq_freq
GOK4_freq_freq

sum(GOK1_freq_freq[,2])
sum(GOK2_freq_freq[,2])
sum(GOK3_freq_freq[,2])
sum(GOK4_freq_freq[,2])
```
